---
title: "BECROPS Pine Data - Compositional Data"
author: "Sergio Diez Hermano"
date: '`r format(Sys.Date(),"%e de %B, %Y")`'
output:
  html_document:
      highlight: tango
      code_folding: show
      toc: yes
      toc_depth: 4
      toc_float:
        collapsed: yes
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
require(knitr)
# include this code chunk as-is to set options
opts_chunk$set(comment = NA, prompt = FALSE, fig.height = 5, fig.width = 5, dpi = 300, fig.align = "center", 
               message = FALSE, warning = FALSE, cache = FALSE, verbose = FALSE)
# Sys.setenv(RSTUDIO_PANDOC = "C:/Program Files/Pandoc")
Sys.setlocale("LC_TIME", "C")
```

# Libraries and functions

```{r}
suppressMessages(library("biomformat"))
suppressMessages(library("tidyr"))      # reshape to long format
suppressMessages(library("pbapply"))
suppressMessages(library("doParallel")) # parallel computing
suppressMessages(library("parallel"))   # parallel computing
suppressMessages(library("dplyr"))      # aggregate counts by taxa
suppressMessages(library("tidyverse"))  # column to row names
suppressMessages(library("openxlsx"))   # create a new Workbook object
suppressMessages(library("xlsx"))       # create a new Workbook object
suppressMessages(library("ggplot2"))
suppressMessages(library("plotrix"))       # draw.circles
suppressMessages(library("ggVennDiagram")) # show in R and fills with color gradient
suppressMessages(library("VennDiagram"))   # don't show directly in R and changes circle size with shared data
suppressMessages(library("ggplotify"))     # grid2grob
suppressMessages(library("ggpubr"))        # ggarrange
suppressMessages(library("viridis"))

#######################
# Rarefaction curves
suppressMessages(library("vegan"))

#######################
# Hill diversity
suppressMessages(library("MeanRarity"))

#######################
# CODA using ZicoSeq
suppressMessages(library("GUniFrac"))

######################
# Phylogeny trees
suppressMessages(library("metacoder"))

######################################################################
# Function to find minimum reads to convert relative to raw abundances

getMin <- function(column, candidates, tol) {
  # Each candidate times vector of relative abundances
  cand.rel <- sapply(candidates, function(x) column*x)
  # Check if generated numbers are integers to a certain tolerance value
  cand.int <- apply(cand.rel, 2, 
                    function(x) sapply(x, 
                                       function(i) min(abs(c(i%%1, i%%1-1))) < 1e-1))
  # Get first candidate that generate an all integers vector
  cand.check <- candidates[which(colSums(cand.int) == length(column))[1]]
  
}

####################################################
# Function to extract taxa ranks from taxonomy list
taxaGet <- function(taxaname, taxranks) {
  taxavec <- character()
  for (i in taxranks) {
    if (i %in% taxaname$rank) {
      taxavec[i] <- taxaname[taxaname$rank == i, 1]
    } else {
      taxavec[i] <- NA
    }
  }
  return(taxavec)
}

########################################
# Function to get color labels for dendrogram
colLab <- function(n) {
  if (is.leaf(n)) {
    a <- attributes(n)
    #labCol <- labelColors[clusMember[which(names(clusMember) == a$label)]]
    labCol <- if (grepl("D", a$label) == TRUE ) "orange" else "purple"
    attr(n, "nodePar") <- c(a$nodePar, lab.col = labCol)
  }
  n
}

########################################
# Estimate intersection between two circles
circle_intersection <- function(x1, y1, r1, x2, y2, r2){
  rr1 <- r1 * r1
  rr2 <- r2 * r2
  d <- sqrt((x2 - x1) * (x2 - x1) + (y2 - y1) * (y2 - y1))
  
  if (d > r2 + r1) # Circles do not overlap
  {
    return(0)
  } else if (d <= abs(r1 - r2) && r1 >= r2){ # Circle2 is completely inside circle1  
    return(pi*rr2)
  } else if (d <= abs(r1 - r2) && r1 < r2){ # Circle1 is completely inside circle2
    return(pi*rr1)
  } else { # Circles partially overlap
    phi <- (acos((rr1 + (d * d) - rr2) / (2 * r1 * d))) * 2
    theta <- (acos((rr2 + (d * d) - rr1) / (2 * r2 * d))) * 2
    area2 <- 0.5 * theta * rr2 - 0.5 * rr2 * sin(theta)
    area1 <- 0.5 * phi * rr1 - 0.5 * rr1 * sin(phi)
    return(area1 + area2)
  }
}
```

# Load data

```{r}
# Tree data
tree.raw <- read.csv("../data/tree_abun.csv", row.names = 1)
tree.taxa <- read.csv("../data/tree_taxa.csv", row.names = 1)
origin.names <- colnames(tree.raw)
colnames(tree.raw) <- paste0(rep("T", ncol(tree.raw)), origin.names)

# Soil data
soil.raw <- read.csv("../data/soil_abun.csv", row.names = 1)
soil.taxa <- read.csv("../data/soil_taxa.csv", row.names = 1)
soil.taxa <- apply(soil.taxa, 2, 
                   function(x) sapply(x, 
                                      function(y) ifelse(grepl("Incertae_sedis", y) == T,
                                                         stringr::str_extract(y, "[^_]+"),
                                                         y))) %>% 
                     as.data.frame

# sapply(soil.taxa$class, function(y) if (grepl("Incertae_sedis", y) == T) stringr::str_extract(y, "[^_]+") else y)

colnames(soil.raw) <- paste0(rep("S", ncol(tree.raw)),origin.names)

# Meta data
meta.data <- read.csv("../data/lifemeta.csv", row.names = 1)
meta.data$UVAshort <- paste0(substr(meta.data$Sample, 1, 1), meta.data$UVAshort)
meta.data$Condition <- gsub("Disease", "Declining", meta.data$Condition)

# Select only soil data
meta.data <- meta.data[meta.data$Type == "Soil", ]
```

# Set taxonomic resolution

## Soil

```{r}
# Select taxonomic level (lowercase)
taxalev <- "genus"

if (taxalev != "species") {
  
  datadup <- soil.raw
  datadup$taxa <- soil.taxa[, taxalev]
  soil.res <- datadup %>% group_by(taxa) %>% summarise(across(everything(), sum)) %>% as.data.frame()
  # soil.res[is.na(soil.res$taxa), "taxa"] <- "unidentified"
  soil.res <- soil.res[-which(soil.res$taxa == "unidentified"), ]
  rownames(soil.res) <- soil.res$taxa
  soil.res <- subset(soil.res, select = -taxa)
  colnames(soil.res) <- meta.data[meta.data$Type == "Soil", "UVAshort"]
  rm(datadup)
  
}

# Get taxonomy
taxcats <- colnames(soil.taxa)
taxo.step <- sapply(rownames(soil.res), function(x) soil.taxa[which(soil.taxa$genus == x)[1],] %>% as.character)
rownames(taxo.step) <- taxcats
taxo.step <- taxo.step[-dim(taxo.step)[1], ] %>% t() %>% as.data.frame()

taxonlist <- list()

for (i in taxcats[1:which(taxcats == taxalev)]) {

  taxonlist[[i]] <- sapply(taxo.step[, i], function(x) paste(substr(i, 1, 1), "__", x, sep=""))

}

taxonframe <- do.call(cbind, taxonlist) %>% as.data.frame(., row.names = rownames(soil.taxa))
soil.taxmap <- soil.res
colnames(soil.taxmap) <- meta.data[meta.data$Sample == "Soil", "UVAshort"]
soil.taxmap$taxonomy <- apply(taxonframe, 1, function(x) paste("r__Root", paste(x, collapse=";"), sep=";"))
soil.taxmap <- cbind(soil.taxmap, taxo.step)

# Save experimental design 
expdes <- table(meta.data$Condition, meta.data$Sample)
sampsiz <- sum(expdes)
condsiz <- sum(expdes[,1])
```

## Folder for results

```{r}
# Folder for results
folder <- paste("its_results/", taxalev,"/zicoseq/", sep="")
if (!dir.exists(folder)) {dir.create(folder, recursive = T)}

# Folder for figs
setwd(folder)
if (!dir.exists("figs")) {dir.create("figs", recursive = T)}
```

# Check counts

```{r}
# Read counts
colSums(soil.res) %>% summary()

# Soil counts per species
for (i in unique(meta.data$Sample)) {
  
  count.sel <- soil.taxmap[, c(which(meta.data$Sample == i), 26:31)]
  count.sel <- count.sel[-which(rowSums(count.sel[,1:6]) == 0), ]
  soil.tax.res <- count.sel[, 7:12]
  
  print(paste(i, "soil counts"))
  
  apply(soil.tax.res[!is.na(soil.tax.res$kingdom), ], 2, function(x) length(unique(x))) %>% print
  
}

# Total soil counts
soil.tax.res <- soil.taxmap[, 26:31]

print("Total soil counts")

apply(soil.tax.res[!is.na(soil.tax.res$kingdom), ], 2, function(x) length(unique(x)))
sort(table(soil.tax.res[!is.na(soil.tax.res$kingdom), "phylum"]), decreasing = T)
sort(table(soil.tax.res[!is.na(soil.tax.res$kingdom), "phylum"])/sum(table(soil.tax.res[!is.na(soil.tax.res$kingdom), "phylum"])), decreasing = T)
```

# Plot tree per type

https://grunwaldlab.github.io/metacoder_documentation/faq.html#the-labels-are-too-small

## Calculations

```{r}
# Global obj
obj <- parse_tax_data(soil.taxmap,
                      class_cols = "taxonomy",
                      class_sep = ";",
                      class_regex = "^([a-z]{0,1})_{0,2}(.*)$",
                      class_key = c("tax_rank" = "taxon_rank", "name" = "taxon_name"))
names(obj$data) <- "otu_counts"
obj <- filter_taxa(obj, taxon_names != "")
obj <- filter_taxa(obj, taxon_names == "Fungi", subtaxa = TRUE)

# Store graphical tree
plot.global <- obj %>% 
  filter_taxa(grepl(pattern = "^[a-zA-Z]+$", taxon_names)) %>% # remove "odd" taxa
  filter_taxa(taxon_ranks == "o", supertaxa = TRUE) %>% # subset to the order rank
  heat_tree(node_label = gsub(pattern = "\\[|\\]", replacement = "", taxon_names),
            node_size = n_obs,
            node_color = n_subtaxa,
            node_color_range = c("#FDE725FF", "#7AD151FF", "#22A884FF", 
                                 "#2A788EFF", "#414487FF"),
            # node_color_interval = c(0, 3),
            # node_color_interval = c(0, 3),
            # node_size_interval = c(0, 500),
            node_label_size_range = c(0.01, 0.025),
            node_color_digits = 0,
            node_size_digits = 0,
            # layout = "davidson-harel", initial_layout = "reingold-tilford",
            tree_label = NA,
            node_size_axis_label = "Size: No. OTUs",
            node_color_axis_label = "Color: No. Subtaxa") +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.17), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.335), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.50), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F)

# Store computed tree by species in a list
sample.objs <- list()

for (i in unique(meta.data$Sample)) {
  
  # All samples from the same species
  sample.taxmap <- soil.taxmap[, c(which(meta.data$Sample == i), (sampsiz+1):(sampsiz+which(taxcats == taxalev)))]
  sample.taxmap <- sample.taxmap[which(rowSums(sample.taxmap[1:condsiz]) > 0), ] 
  sample.obj <- parse_tax_data(sample.taxmap,
                            class_cols = "taxonomy",
                            class_sep = ";",
                            class_regex = "^([a-z]{0,1})_{0,2}(.*)$",
                            class_key = c("tax_rank" = "taxon_rank", "name" = "taxon_name"))
  names(sample.obj$data) <- "otu_counts"
  sample.obj <- filter_taxa(sample.obj, taxon_names != "")
  sample.obj <- filter_taxa(sample.obj, taxon_names == "Fungi", subtaxa = TRUE)
  sample.objs[[i]] <- sample.obj
  
}

# Store graphical tree
plot.trees <- list()

for (i in unique(meta.data$Sample)) {
  
  plot.trees[[i]] <- sample.objs[[i]] %>% 
    filter_taxa(grepl(pattern = "^[a-zA-Z]+$", taxon_names)) %>% # remove "odd" taxa
    filter_taxa(taxon_ranks == "o", supertaxa = TRUE) %>% # subset to the order rank
    heat_tree(node_label = gsub(pattern = "\\[|\\]", replacement = "", taxon_names),
              node_size = n_obs,
              node_color = n_subtaxa,
              node_color_range = c("#FDE725FF", "#7AD151FF", "#22A884FF", 
                                   "#2A788EFF", "#414487FF"),
              # node_color_interval = c(0, 3),
              # node_color_interval = c(0, 3),
              node_size_interval = c(0, 500),
              node_label_size_range = c(0.01, 0.02),
              node_color_digits = 0,
              node_size_digits = 0,
              # layout = "davidson-harel", initial_layout = "reingold-tilford",
              tree_label = NA,
              node_size_axis_label = "Size: No. OTUs",
              node_color_axis_label = "Color: No. Subtaxa") +
    ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.17), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                         inherit.aes = FALSE, show.legend = F) +
    ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.335), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                         inherit.aes = FALSE, show.legend = F) +
    ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.50), colour = alpha("darkgrey", 0.5), linetype = "dashed", 
                         inherit.aes = FALSE, show.legend = F)
  
  
}

```

## Plot trees

```{r, fig.width=10, fig.height=10}
# Global tree
png(filename=paste(folder, "/figs/tree_aglobal.png", sep=""), type="cairo",
    units="in", width=8, height=6, pointsize=12,
    res=300)

print(plot.global)

dev.off()

# Tree per species
for (i in unique(meta.data$Sample)) {
  
  png(filename=paste(folder, "/figs/tree_", i, ".png", sep=""), type="cairo",
      units="in", width=8, height=6, pointsize=12,
      res=300)
  
  print(plot.trees[[i]])
  
  dev.off()
  
}

```

# Rarefaction curves

```{r, fig.width=20, fig.height=5}
# goodcov <- QsRutils::goods(t(soil.res))
raredata <- soil.res

## Parallelize multiple cores
no_cores <- detectCores(logical = TRUE); cl <- makeCluster(no_cores-1); registerDoParallel(cl)

par(mfrow=c(1,4), cex = 1.2)

rarelist <- list()
for (i in unique(meta.data$Sample)) {
  
  colselec <- meta.data[meta.data$Sample == i, "UVAshort"]
  rarelist[[i]] <- rarecurve(t(raredata[ , colselec]), step = 10, col = c(rep("orange", condsiz/2), rep("purple", condsiz/2)), 
                             lwd = 1.5,  main = i)

  
}

```

## Save plots

```{r, fig.width=15, fig.height=5.5}
png(filename=paste(folder, "figs/rarefaction_curves.png", sep=""), type="cairo",
      units="in", width=15, height=5.5, pointsize=12,
      res=300)

# Set layout for 5 plots and legend at the bottom
layout(mat = matrix(c(1,2,3,4,5,6,6,6,6,6), nrow = 2, ncol = 5, byrow = TRUE), heights = c(5.5, 0.5), widths = c(0.7,4,4,4,4))
# Size of labels and margins of each plot
par(cex = 1.2, mai = c(1, 0.3, 0.8, 0.1))
# Empty plot to write a single ylab at the beginning
plot(NULL, xlim = c(0,1), ylim = c(0,1), yaxt="n", xaxt="n", bty = "n", ylab = NA, xlab = NA)
title(ylab="No. of Genera", line=0)

# Common y-axis upper limit
upY <- sapply(rarelist, 
              function(x) sapply(x, function(y) y[length(y)])) %>% max()

# Plot
for (i in unique(meta.data$Sample)) {
  
  # Get upper axis limits
  upX <- sapply(rarelist[[i]], function(x) names(x[length(x)])) %>% 
    gsub(pattern = "N", replacement = "") %>%
    as.numeric() %>%
    max()
  # upY <- sapply(rarelist[[i]], function(x) x[length(x)]) %>%
  #   max()
  
  if (i == unique(meta.data$Sample)[1]) {
    
    # Empty plot
    plot(NULL, xlim = c(1, upX), ylim = c(0, upY), 
         ylab = NA, xlab = NA, main = i, yaxt = "n")
    axis(2, at = seq(0,upY,50), labels = seq(0,upY,50))
    title(xlab="Sample size", line=2.5)

    # Background grid
    grid()
    # Counter for color
    countcol <- 1
    
    # Subset replicate
    rareplot <- rarelist[[i]]
    for (j in rareplot) {
      xaxis <- as.numeric(gsub("N", "", names(j)))
      lines(xaxis, j, lwd = 3, col = if (countcol <= condsiz/2) "orange" else "purple")
      countcol <- countcol + 1
    }
    
  } else {
    
    # Empty plot
    plot(NULL, xlim = c(1, upX), ylim = c(0, upY), 
         ylab = NA, xlab = NA, main = i, yaxt = "n")
    axis(2, at = seq(0,upY,50), labels = FALSE)
    title(xlab="Sample size", line=2.5)

    # Background grid
    grid()
    # Counter for color
    countcol <- 1
    
    # Subset replicate
    rareplot <- rarelist[[i]]
    for (j in rareplot) {
      xaxis <- as.numeric(gsub("N", "", names(j)))
      lines(xaxis, j, lwd = 3, col = if (countcol <= condsiz/2) "orange" else "purple")
      countcol <- countcol + 1
    }
    
  }
 
  
}

# Plot legend at the bottom
par(mai=c(0,0,0,0))
plot.new()
legend(x="center", ncol=2, bty = "n", legend=c("Declining", "Healthy"),
       fill=c("orange","purple"))

dev.off()
```

## Common x axis

```{r, fig.width=16, fig.height=5.5}

png(filename=paste(folder, "figs/rarefaction_curves_commonX.png", sep=""), type="cairo",
       units="in", width=15, height=5.5, pointsize=12,
      res=300)

# Set layout for 5 plots and legend at the bottom
layout(mat = matrix(c(1,2,3,4,5,6,6,6,6,6), nrow = 2, ncol = 5, byrow = TRUE), heights = c(5.5, 0.5), widths = c(0.7,4,4,4,4))
# Size of labels and margins of each plot
par(cex = 1.2, mai = c(1, 0.3, 0.8, 0.1))
# Empty plot to write a single ylab at the beginning
plot(NULL, xlim = c(0,1), ylim = c(0,1), yaxt="n", xaxt="n", bty = "n", ylab = NA, xlab = NA)
title(ylab="No. of Genera", line=0)

# Common x and y-axis upper limit
upY <- sapply(rarelist, 
              function(x) sapply(x, function(y) y[length(y)])) %>% max()

upX <- sapply(rarelist, 
              function(y) sapply(y, function(x) names(x[length(x)]))) %>% 
  gsub(pattern = "N", replacement = "") %>%
  as.numeric() %>%
  max()

# Plot
for (i in unique(meta.data$Sample)) {
  
  # Get upper axis limits
  # upX <- sapply(rarelist[[i]], function(x) names(x[length(x)])) %>% 
  #   gsub(pattern = "N", replacement = "") %>%
  #   as.numeric() %>%
  #   max()
  # upY <- sapply(rarelist[[i]], function(x) x[length(x)]) %>%
  #   max()
  
  if (i == unique(meta.data$Sample)[1]) {
    
    # Empty plot
    plot(NULL, xlim = c(1, upX), ylim = c(0, upY), 
         ylab = NA, xlab = NA, main = i, yaxt = "n")
    axis(2, at = seq(0,upY,50), labels = seq(0,upY,50))
    title(xlab="Sample size", line=2.5)

    # Background grid
    grid()
    # Counter for color
    countcol <- 1
    
    # Subset replicate
    rareplot <- rarelist[[i]]
    for (j in rareplot) {
      xaxis <- as.numeric(gsub("N", "", names(j)))
      lines(xaxis, j, lwd = 3, col = if (countcol <= condsiz/2) "orange" else "purple")
      countcol <- countcol + 1
    }
    
  } else {
    
    # Empty plot
    plot(NULL, xlim = c(1, upX), ylim = c(0, upY), 
         ylab = NA, xlab = NA, main = i, yaxt = "n")
    axis(2, at = seq(0,upY,50), labels = FALSE)
    title(xlab="Sample size", line=2.5)

    # Background grid
    grid()
    # Counter for color
    countcol <- 1
    
    # Subset replicate
    rareplot <- rarelist[[i]]
    for (j in rareplot) {
      xaxis <- as.numeric(gsub("N", "", names(j)))
      lines(xaxis, j, lwd = 3, col = if (countcol <= condsiz/2) "orange" else "purple")
      countcol <- countcol + 1
    }
    
  }
 
  
}

# Plot legend at the bottom
par(mai=c(0,0,0,0))
plot.new()
legend(x="center", ncol=2, bty = "n", legend=c("Declining", "Healthy"),
       fill=c("orange","purple"))

dev.off()
```

# Venn diagram

```{r, fig.width=5, fig.height=5}
# Get sample categories and frequencies
catsamp <- gsub("[[:digit:]]", "", colnames(soil.res)) %>% table
criteria <- 10

# Per tree species
vennParcList <- list()

for (k in unique(meta.data$Condition)) {
  
  selectcol <- which(meta.data$Condition == k)
  vennParcList[[k]] <- apply(soil.res[, selectcol], 1, function(x) length(which(x != 0))) %>% t
  
}


vennParcList.names <- lapply(vennParcList, function(x) colnames(x)[x >= criteria])

# Helper function to display Venn diagram
display_venn <- function(x, ...){
  grid.newpage()
  venn_object <- venn.diagram(x, filename = NULL, disable.logging = TRUE, ...)
  grid.draw(venn_object)
}

png(filename=paste(folder, "figs/venn_diagram.png", sep=""), type="cairo",
      units="in", width=6, height=6, pointsize=12,
      res=300)

display_venn(vennParcList.names,
             # category.names = names(vennParcList.names),
             category.names = "",
             # cat.default.pos = "outer",
             cat.col = c("orange", "purple"),
             col = c("orange", "purple"),
             fill = c(alpha("orange",0.3), alpha('purple',0.3)),
             print.mode = c("raw", "percent"),
             fontfamily = "Helvetica",
             cat.fontfamily = "Helvetica",
             margin = 0.05)

dev.off()

```

## Save excel

```{r}
# Get intersections
intervenn <- gplots::venn(vennParcList.names, show.plot = FALSE)
intervenn <- attributes(intervenn)$intersections
names(intervenn) <- gsub(":", ".", names(intervenn))

# Save excel
wb <- createWorkbook()

for (i in names(intervenn)) {
  
    sheet <- createSheet(wb, i)
    addDataFrame(intervenn[[i]], sheet=sheet, startColumn=1, row.names=TRUE, showNA = T)
    
}

saveWorkbook(wb, paste0(folder, "venn_genera.xlsx"))

```


# Hill diversity

Source code and explanations: https://mikeroswell.github.io/MeanRarity/articles/Using_MeanRarity.html

- effective number of rare species, S (l= 1, q=0, species richness), 
- effective number of common species, eH' (l = 0, q=1, Shannon diversity or exponential or Shannon entropy), 
- effective number of highly abundant species, 1/D (l = -1, q=2, Simpson diversity or the inverse of Simpson concentration)
  
```{r}
# Vector for "l" exponent values
hillexps <- seq(-1, 1, 0.01)

# Estimate Hill diversity per sample and for every "l" value
hillframe <- as.data.frame(t(apply(soil.res, 2, function(x) sapply(hillexps, function(y) rarity(x, y)))))

# Add "l" values as column names
colnames(hillframe) <- hillexps

# Add variables data (sampling site, health status)
hillframe.var <- cbind(meta.data, hillframe)

# Long format to ease plotting
hillframe.long <- hillframe.var %>% gather(Hill, value, -(1:10))
hillframe.long$Hill <- as.numeric(hillframe.long$Hill)
hillframe.long$UVAshort <- as.factor(hillframe.long$UVAshort)
hillframe.long$Sample <- as.factor(hillframe.long$Sample)
hillframe.long$Sample <- as.factor(hillframe.long$Sample)
hillframe.long$Condition <- as.factor(hillframe.long$Condition)
```

## Save plot lines

```{r, fig.width=15, fig.height=6}

png(filename=paste(folder, "figs/hill_diversity_lines.png", sep=""), type="cairo",
      units="in", width=15, height=6.5, pointsize=12,
      res=300)

# Set layout for 4 plots and legend at the bottom
layout(mat = matrix(c(1,2,3,4,5,6,6,6,6,6), nrow = 2, ncol = 5, byrow = TRUE), heights = c(5.5, 1), widths = c(0.7,4,4,4,4))
# Size of labels and margins of each plot
par(cex = 1.5, mai = c(1, 0.3, 0.8, 0.1))
# Empty plot to write a single ylab at the beginning
plot(NULL, xlim = c(0,1), ylim = c(0,1), yaxt="n", xaxt="n", bty = "n", ylab = NA, xlab = NA)
title(ylab="No. of Genera", line=0)


# Plot
for (i in unique(hillframe.long$Sample)) {
  
  if (i == unique(meta.data$Sample)[1]) {
    
    # Empty plot
    plot(NULL, xlim = c(-1, 1), ylim = c(0, max(hillframe.long$value)),
         yaxt = "n", ylab = NA, xlab = NA, main = i)
    axis(2, at = seq(0,250,50), labels = seq(0,250,50))
    title(xlab = "Hill diversity", line=2.5)
    
    # Background grid
    grid()
    # Subset sampling site
    Sampleplot <- hillframe.long[hillframe.long$Sample == i, ]
    
    for (j in unique(hillframe.long$UVAshort)) {
      
      # Subset replicate
      uvaplot <- Sampleplot[Sampleplot$UVAshort == j, ]
      
      for (k in unique(hillframe.long$Condition)) {
        
        # Subset status and plot
        condiplot <- uvaplot[uvaplot$Condition == k, ]
        lines(condiplot$Hill, condiplot$value, lwd = 3, 
              col = if (k == "Declining") "orange" else "purple")
        
      }
      
    } 
    
  } else {
    
    # Empty plot
    plot(NULL, xlim = c(-1, 1), ylim = c(0, max(hillframe.long$value)), 
         yaxt = "n", ylab = NA, xlab = NA, main = i)
    axis(2, at = seq(0, 250, 50), labels = FALSE)
    title(xlab = "Hill diversity", line=2.5)
    # Background grid
    grid()
    # Subset sampling site
    Sampleplot <- hillframe.long[hillframe.long$Sample == i, ]
    
    for (j in unique(hillframe.long$UVAshort)) {
      
      # Subset replicate
      uvaplot <- Sampleplot[Sampleplot$UVAshort == j, ]
      
      for (k in unique(hillframe.long$Condition)) {
        
        # Subset status and plot
        condiplot <- uvaplot[uvaplot$Condition == k, ]
        lines(condiplot$Hill, condiplot$value, lwd = 3, 
              col = if (k == "Declining") "orange" else "purple")
        
        
      }
      
    }
    
  }
  
}

# Plot legend at the bottom
par(mai=c(0,0,0,0))
plot.new()
legend(x="center", ncol=2, bty = "n", legend=c("Declining", "Healthy"),
       fill=c("orange","purple"))

dev.off()

```

## Save average plot lines

```{r, fig.width=15, fig.height=6}

png(filename=paste(folder, "figs/hill_diversity_lines_average.png", sep=""), type="cairo",
      units="in", width=15, height=6.5, pointsize=12,
      res=300)

# Set layout for 4 plots and legend at the bottom
layout(mat = matrix(c(1,2,3,4,5,6,6,6,6,6), nrow = 2, ncol = 5, byrow = TRUE), heights = c(5.5, 1), widths = c(0.7,4,4,4,4))
# Size of labels and margins of each plot
par(cex = 1.5, mai = c(1, 0.3, 0.8, 0.1))
# Empty plot to write a single ylab at the beginning
plot(NULL, xlim = c(0,1), ylim = c(0,1), yaxt="n", xaxt="n", bty = "n", ylab = NA, xlab = NA)
title(ylab="No. of Genera", line=0)


# Plot
for (i in unique(hillframe.long$Sample)) {
  
  if (i == unique(meta.data$Sample)[1]) {
    
    # Empty plot
    plot(NULL, xlim = c(-1, 1), ylim = c(0, max(hillframe.long$value)),
         yaxt = "n", ylab = NA, xlab = NA, main = i)
    axis(2, at = seq(0,250,50), labels = seq(0,250,50))
    title(xlab = "Hill diversity", line=2.5)
    
    # Background grid
    grid()
    # Subset sampling site
    Sampleplot <- hillframe.long[hillframe.long$Sample == i, ]
    
    for (k in unique(hillframe.long$Condition)) {
      
      # Subset status and plot
      condiplot <- Sampleplot[Sampleplot$Condition == k, ]
      # Estimate mean
      mean.condiplot <- aggregate(value ~ Hill, condiplot, mean)
      sd.condiplot <- aggregate(value ~ Hill, condiplot, function(x) sd(x)/sqrt(3))
      polygon(x = c(sd.condiplot$Hill, rev(sd.condiplot$Hill)), 
              y = c(mean.condiplot$value + sd.condiplot$value, rev(mean.condiplot$value - sd.condiplot$value)), 
              col = if (k == "Declining") scales::alpha("orange", 0.2) else scales::alpha("purple", 0.2),
              border = NA)
      lines(mean.condiplot$Hill, mean.condiplot$value, lwd = 3, col = if (k == "Declining") "orange" else "purple")
      
      
    } 
    
  } else {
    
    # Empty plot
    plot(NULL, xlim = c(-1, 1), ylim = c(0, max(hillframe.long$value)), 
         yaxt = "n", ylab = NA, xlab = NA, main = i)
    axis(2, at = seq(0, 250, 50), labels = FALSE)
    title(xlab = "Hill diversity", line=2.5)
    # Background grid
    grid()
    # Subset sampling site
    Sampleplot <- hillframe.long[hillframe.long$Sample == i, ]
    
    for (k in unique(hillframe.long$Condition)) {
      
      # Subset status and plot
      condiplot <- Sampleplot[Sampleplot$Condition == k, ]
      # Estimate mean
      mean.condiplot <- aggregate(value ~ Hill, condiplot, mean)
      sd.condiplot <- aggregate(value ~ Hill, condiplot, function(x) sd(x)/sqrt(3))
      polygon(x = c(sd.condiplot$Hill, rev(sd.condiplot$Hill)), 
              y = c(mean.condiplot$value + sd.condiplot$value, rev(mean.condiplot$value - sd.condiplot$value)), 
              col = if (k == "Declining") scales::alpha("orange", 0.2) else scales::alpha("purple", 0.2),
              border = NA)
      lines(mean.condiplot$Hill, mean.condiplot$value, lwd = 3, col = if (k == "Declining") "orange" else "purple")
      
    }
    
  }
  
}

# Plot legend at the bottom
par(mai=c(0,0,0,0))
plot.new()
legend(x="center", ncol=2, bty = "n", legend=c("Declining", "Healthy"),
       fill=c("orange","purple"))

dev.off()

```

# Running ZicoSeq

Tutorial source: https://cran.r-project.org/web/packages/GUniFrac/vignettes/ZicoSeq.html

```{r}

zico.list <- list()
meta.list <- list()

set.seed(123456)
for (i in unique(meta.data$Sample)) {
  
  # Subset samples in abundance matrix according to first letter of i
  res.to.zico <- as.matrix(soil.res[, which(meta.data$Sample == i)])
  res.to.zico <- res.to.zico[-which(rowSums(res.to.zico) == 0), ]
  meta.to.zico <- meta.data[meta.data$Sample == i, ]
  
  # Run ZicoSeq
  zico.list[[i]] <- ZicoSeq(meta.dat = meta.to.zico, feature.dat = res.to.zico, 
                         grp.name = 'Condition', adj.name = NULL, 
                         feature.dat.type = "count",
                         # Filter to remove rare taxa
                         prev.filter = 0.2, mean.abund.filter = 0,  
                         max.abund.filter = 0.002, min.prop = 0, 
                         # Winsorization to replace outliers
                         is.winsor = TRUE, outlier.pct = 0.1, 
                         winsor.end = 'top',
                         # Posterior sampling 
                         is.post.sample = TRUE, post.sample.no = 25, 
                         # Use the square-root transformation
                         link.func = list(function (x) x^0.5), 
                         stats.combine.func = max,
                         # Permutation-based multiple testing correction
                         perm.no = 500,  strata = NULL, 
                         # Reference-based multiple stage normalization
                         ref.pct = 0.5, stage.no = 12, excl.pct = 0.2,
                         # Family-wise error rate control
                         is.fwer = TRUE, verbose = TRUE, 
                         return.feature.dat = T)
  # Store meta
  meta.list[[i]] <- meta.to.zico
  
}

saveRDS(list(zico.list = zico.list, meta.list = meta.list), paste0(folder, "/zicoResults.RDS"))

```

## Save excel

```{r}
# Per species
sig.feat.list <- list()

for (i in unique(meta.data$Sample)) {
  
  # Select genres with adjusted pval < 0.1
  sig.features <- which(zico.list[[i]]$p.adj.fdr < 0.1)
  
  # Negative R2 means more abundant in Declining samples
  pval.r2 <- data.frame(pval = zico.list[[i]]$p.adj.fdr[sig.features],
                        r2 = zico.list[[i]]$R2[sig.features]*sign(zico.list[[i]]$coef.list[[1]][2,sig.features]))
  
  # Store in a list
  sig.feat.list[[i]] <- pval.r2
  
}


# Save excel
wb <- createWorkbook()

for (i in unique(meta.data$Sample)) {
  
    sheet <- createSheet(wb, i)
    addDataFrame(sig.feat.list[[i]], sheet=sheet, startColumn=1, row.names=TRUE, showNA = T)
    
}

saveWorkbook(wb, paste0(folder, "zicoseq_pvals_r2.xlsx"))

```


## Volcano plot

```{r, fig.width=15}
loadlist <- readRDS(paste0(folder, "/zicoResults.RDS"))
zico.list <- loadlist$zico.list
meta.list <- loadlist$meta.list

plotlist <- lapply(1:4, function(x) ZicoSeq.plot(zico.list[[x]], meta.list[[x]], pvalue.type = 'p.adj.fdr', 
                                                 cutoff = 0.1, text.size = 8,
                                                 out.dir = NULL, width = 8, height = 8) +
                     ylim(0, 4) +
                     xlim(-0.3, 0.3) +
                     # geom_hline(yintercept=-log(0.1,10), linetype="dashed", color = "gray", lwd = 1) +
                     # geom_hline(yintercept=-log(0.05,10), linetype="dashed", color = "red", lwd = 1) +
                     # geom_hline(yintercept=-log(0.01,10), linetype="dashed", color = "purple", lwd = 1) +
                     # geom_vline(xintercept= -0.1, linetype="dotted", color = "orange", lwd = 1) +
                     # geom_vline(xintercept= 0.1, linetype="dotted", color = "purple", lwd = 1) +
                     # coord_cartesian(ylim = c(0, 4), clip = "off") +
                     # annotate("text", x = -0.25, y = 4.2, label = "Declining") +
                     # annotate("text", x = 0.25, y = 4.2, label = "Healthy") +
                     geom_text(x=-0.25, y=4.05, label="Declining", col = "darkgrey", size = 5) +
                     geom_text(x=0.25, y=4.05, label="Healthy", col = "darkgrey", size = 5) +
                     ggtitle(names(zico.list)[x]) +
                     theme(plot.title = element_text(hjust = 0.5, size = 18),
                           axis.text=element_text(size=12),
                           axis.title=element_text(size=14),
                           legend.title=element_text(size=12),
                           legend.text=element_text(size=12)))
         # theme(plot.title = element_text(hjust = 0.5),
         #       panel.grid.major = element_blank(), panel.grid.minor = element_blank()))

png(filename=paste(folder, "/figs/zicoseq.png", sep=""), type="cairo",
    units="in", width=10, height=10, pointsize=12,
    res=300)
  
ggarrange(plotlist = plotlist, ncol = 2, nrow = 2, common.legend = T)

dev.off()

# ZicoSeq.plot(ZicoSeq.obj, meta.to.zico, pvalue.type = 'p.adj.fdr', 
#              cutoff = 0.1, text.size = 10,
#              out.dir = NULL, width = 8, height = 8) +
#   ggtitle("Hola") +
#   theme(plot.title = element_text(hjust = 0.5))

```

## Trees

### Calculations

```{r, fig.width=8, fig.height=6}

set.seed(12345)
vircols <- viridis(5)

# Get all taxonomy names involved in zicoseq
all.names <- list()

for (i in unique(meta.data$Sample)) {
  
  all.names[[i]] <- names(zico.list[[i]]$p.adj.fdr)
  
}


# Unique
all.names.vec <-  unlist(all.names) %>% unique
all.names.num <- rep(0, length(all.names.vec))
names(all.names.num) <- all.names.vec
aa <- soil.taxmap[which(rownames(soil.taxmap) %in% all.names.vec), ]

###############
# Empty tree
cc <- data.frame(r2 = all.names.num, aa[25:31])

# All samples from the same species
sample.obj <- parse_tax_data(cc,
                             class_cols = "taxonomy", # the column that contains taxonomic information
                             class_sep = ";", # The character used to separate taxa in the classification
                             class_regex = "^(.+)__(.+)$", # Regex identifying where the data for each taxon is
                             class_key = c(tax_rank = "info", # A key describing each regex capture group
                                           tax_name = "taxon_name"))
sample.obj <- filter_taxa(sample.obj, taxon_names == "Fungi", subtaxa = TRUE)
sample.obj$data$tax_abund <- calc_taxon_abund(sample.obj, "tax_data",
                                              cols = "r2")

colnames(sample.obj$data$tax_abund) <- c("taxon_id", "R2")
empty.tree <- sample.obj %>% heat_tree(node_label = gsub(pattern = "\\[|\\]", replacement = "", taxon_names),
                                       node_size = n_subtaxa,
                                       node_size_range = c(0.01, 0.03),
                                       node_color = R2,
                                       node_color_interval = c(-0.5, 0.5),
                                       node_color_range = c("orange", alpha("lightgray",0.2), "purple"),
                                       node_label_color = "black",
                                       # node_label_size = abs(R2),
                                       node_label_size_range = c(0.012, 0.025),
                                       tree_label = NA,
                                       make_node_legend = F,
                                       layout = "reingold-tilford") +
  # initial_layout = "reingold-tilford") +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.10), colour = alpha(vircols[1], 0.2), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.20), colour = alpha(vircols[2], 0.2), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.30), colour = alpha(vircols[3], 0.2), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.40), colour = alpha(vircols[4], 0.2), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F) +
  ggforce::geom_circle(aes(x0 = 0.5, y0 = 0.5, r = 0.50), colour = alpha(vircols[5], 0.2), linetype = "dashed", 
                       inherit.aes = FALSE, show.legend = F)

######################
# Coloured trees
plot.tree.zico <- list()

  for (i in unique(meta.data$Sample)) {

    # Bind R2 from ZicoSeq with taxonomic data
    r2 <- sapply(1:length(zico.list[[i]]$p.adj.fdr), 
                 function(x) ifelse(zico.list[[i]]$p.adj.fdr[x] < 0.1, 
                                    zico.list[[i]]$R2[x]*sign(zico.list[[i]]$coef.list[[1]][2,x]),
                                    0))
    
    r2 <- tapply(c(all.names.num, r2), names(c(all.names.num, r2)), sum)
    # names(r2) <- names(zico.list[[h]][[i]]$p.adj.fdr)
    cc <- cbind(r2, aa[25:31])
    
    # Assign a 0 to R2 bellow abs(0.1)
    cc$r2 <- sapply(cc$r2, function(x) ifelse(abs(x) < 0.1, 0, x))
    
    # All samples from the same species
    sample.obj <- parse_tax_data(cc,
                                 class_cols = "taxonomy", # the column that contains taxonomic information
                                 class_sep = ";", # The character used to separate taxa in the classification
                                 class_regex = "^(.+)__(.+)$", # Regex identifying where the data for each taxon is
                                 class_key = c(tax_rank = "info", # A key describing each regex capture group
                                               tax_name = "taxon_name"))
    sample.obj <- filter_taxa(sample.obj, taxon_names == "Fungi", subtaxa = TRUE)
    sample.obj$data$tax_abund <- calc_taxon_abund(sample.obj, "tax_data",
                                                  cols = "r2")
    
    colnames(sample.obj$data$tax_abund) <- c("taxon_id", "R2")
    plot.tree.zico[[i]] <- sample.obj %>% heat_tree(node_label = NA,
                                                    node_size = n_subtaxa,
                                                    node_size_range = c(0.01, 0.03),
                                                    node_color = R2,
                                                    node_color_interval = c(-0.5, 0.5),
                                                    node_color_range = c("orange", alpha("lightgray",0.2), "purple"),
                                                    # node_label_size = abs(R2),
                                                    # node_label_size_range = c(0.01, 0.02),
                                                    tree_label = NA,
                                                    make_node_legend = F,
                                                    layout = "reingold-tilford")
    
  }




```


### Plot trees

```{r}
# Plot empty tree
png(filename=paste(folder, "/figs/zicotree_empty.png", sep=""), type="cairo",
    units="in", width=8, height=6, pointsize=12,
    res=300)

print(empty.tree)

dev.off()


# Plot coloured trees
  for (i in unique(meta.data$Sample)) {
    
    png(filename=paste(folder, "/figs/zicotree_", i, ".png", sep=""), type="cairo",
        units="in", width=8, height=6, pointsize=12,
        res=300)
    
    print(plot.tree.zico[[i]])
    
    dev.off()
    
  }

```
### Individual coloured trees

```{r}
######################
# Coloured trees
plot.tree.zico <- list()

  for (i in unique(meta.data$Sample)) {

    # Bind R2 from ZicoSeq with taxonomic data
    r2 <- sapply(1:length(zico.list[[i]]$p.adj.fdr), 
                 function(x) ifelse(zico.list[[i]]$p.adj.fdr[x] < 0.1, 
                                    zico.list[[i]]$R2[x]*sign(zico.list[[i]]$coef.list[[1]][2,x]),
                                    0))
    
    r2 <- tapply(c(all.names.num, r2), names(c(all.names.num, r2)), sum)
    # names(r2) <- names(zico.list[[i]]$p.adj.fdr)
    cc <- cbind(r2, aa[25:31])
    
    # Assign a 0 to R2 bellow abs(0.1)
    cc$r2 <- sapply(cc$r2, function(x) ifelse(abs(x) < 0.1, 0, x))
    
    # All samples from the same species
    sample.obj <- parse_tax_data(cc,
                                 class_cols = "taxonomy", # the column that contains taxonomic information
                                 class_sep = ";", # The character used to separate taxa in the classification
                                 class_regex = "^(.+)__(.+)$", # Regex identifying where the data for each taxon is
                                 class_key = c(tax_rank = "info", # A key describing each regex capture group
                                               tax_name = "taxon_name"))
    sample.obj <- filter_taxa(sample.obj, taxon_names == "Fungi", subtaxa = TRUE)
    sample.obj$data$tax_abund <- calc_taxon_abund(sample.obj, "tax_data",
                                                  cols = "r2")
    
    colnames(sample.obj$data$tax_abund) <- c("taxon_id", "R2")
    plot.tree.zico[[i]] <- sample.obj %>% heat_tree(node_label = gsub(pattern = "\\[|\\]", replacement = "", taxon_names),
                                                    node_size = n_subtaxa,
                                                    node_size_range = c(0.01, 0.03),
                                                    node_color = R2,
                                                    node_color_interval = c(-0.5, 0.5),
                                                    node_color_range = c("orange", alpha("lightgray",0.2), "purple"),
                                                    node_label_color = ifelse(sample.obj$data$tax_abund$R2 != 0, "black", NA),
                                                    node_label_size = abs(R2),
                                                    node_label_size_range = c(0.01, 0.02),
                                                    tree_label = NA,
                                                    make_node_legend = F,
                                                    layout = "reingold-tilford",
                                                    title = i)
    
  }


# Plot trees

# Plot coloured trees

  for (i in unique(meta.data$Sample)) {
    
    png(filename=paste(folder, "/figs/zicotree_names_", h, "_", i, ".png", sep=""), type="cairo",
        units="in", width=8, height=6, pointsize=12,
        res=300)
    
    print(plot.tree.zico[[i]])
    
    dev.off()
    
  }


```

# Fungal traits {.tabset .tabset-fade .tabset-pills}

## Estimate

```{r}
# Read fungal traits csv
fungalTraits <- read.csv("../../FungalTraits 1.2_ver_16Dec_2020 - V.1.2.csv")
traits24 <- fungalTraits[fungalTraits$GENUS %in% rownames(soil.res), c("GENUS", "primary_lifestyle")] 

# Add abundancy information
traits24 <- cbind(traits24, soil.res[match(traits24$GENUS, rownames(soil.res)), ])
traits24$primary_lifestyle <- gsub("unspecified_", "", traits24$primary_lifestyle)
traits24$primary_lifestyle <- gsub("_", " ", traits24$primary_lifestyle)
traits24$primary_lifestyle <- as.factor(traits24$primary_lifestyle)

# Select sampling site declined/healthy and sum
# Add 1 to avoid -Inf in log transformation
sampsite.list <- list()

for (i in c("L", "V", "A", "C")) {
  
  sampsite.dec <- traits24[, grep(paste0(i, "D"), colnames(traits24))] %>% rowsum(., group = traits24$primary_lifestyle) + 1
  sampsite.hel <- traits24[, grep(paste0(i, "H"), colnames(traits24))] %>% rowsum(., group = traits24$primary_lifestyle) + 1
  sampsite.list[[i]] <- list(Declining = sampsite.dec, Healthy = sampsite.hel)
  
}

names(sampsite.list) <- c("Chestnut", "Cork oak", "Holm oak", "Pyrenean oak")



```

## Lollipop plot 

```{r, fig.width=16, fig.height=12}

# par(mfrow=c(2,2))

png(filename=paste(folder, "figs/functional_lollipop.png", sep=""), type="cairo",
      units="in", width=16, height=14, pointsize=12,
      res=300)

layout(mat = matrix(c(1,2,3,4,5,5), nrow = 3, ncol = 2, byrow = TRUE), heights = c(6, 6, 0.5), widths = c(8,8))
# par(cex = 1.8, mai = c(1.6, 0.3, 0.8, 0.1))

for (i in c("Chestnut", "Cork oak", "Holm oak", "Pyrenean oak")) {
  
  # Extract data from list
  sitesel <- sampsite.list[[i]]
  absum.h <- sitesel$Healthy %>% log(., 2) %>% rowSums()
  absum.h <- absum.h/sum(absum.h)
  absum.d <- sitesel$Declining %>% log(., 2) %>% rowSums()
  absum.d <- absum.d/sum(absum.d)
  
  # Order by Declining importance
  absum.h <- absum.h[order(absum.d)]
  absum.h <- absum.h[names(absum.h) != ""]
  absum.d <- absum.d[order(absum.d)]
  absum.d <- absum.d[names(absum.d) != ""]
  numtraits <- length(absum.h)
  
  # Plot
  par(mgp=c(2,1,0), mar=c(4, 10, 2, 1), cex = 1.2)
  plot(rep(0, numtraits), 1:numtraits, xlim = c(0, max(c(absum.h, absum.d))), col = "white", yaxt = "n", 
       ylab = "", xlab = "log2(abundance)", main = i)
  # title(xlab="log2(abundance)", line=2, cex.lab=1.2)
  axis(side = 2, at =  1:numtraits, labels = names(absum.h), las = 2)
  segments(x0 = absum.d, y0 = 1:numtraits, x1 = absum.h, y1 = 1:numtraits)
  points(absum.d, 1:numtraits, pch=19, col = "orange")
  points(absum.h, 1:numtraits, pch=19, col = "purple")
  
  
}

# Plot legend at the bottom
par(mai=c(0,0,0,0), cex = 1.5)
plot.new()
legend(x="center", ncol=2, bty = "n", legend=c("Declining", "Healthy"),
       fill=c("orange","purple"))

dev.off()

```

